---
title: "Assignment 6 - Midterm Proposal (2 pts)"
author: "TYPE YOUR NAME HERE (UVA computing ID)"
date: "Due Date: 11:59pm, Feb 15"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: hide
  pdf_document:
    toc: yes
---

<style>
h1.title {
  font-size: 30px;
}
h1 {
  font-size: 26px;
}
h2 {
  font-size: 22px;
}
h3 { 
  font-size: 18px;
}

</style>

For the midterm proposal, briefly describe your topic along with both an article/report/blog and a dataset. *Submit both `.Rmd` and "knitted"`.html` files*

# Article

- Include a link to access your article. 

- Provide your presentation title. It can be the same as the title of your article. Or, you can modify the title.

# Data

- Describe your dataset that is relevant, related to, and informative of the article.

- Print the first 6 rows using function `head()`.

```{r}

```


# Data Validation

- Check the content of the attributes, traits, features, rows, and/or other properties specific to your dataset.

   + Is the data type correct for this field?

   + Is the value within the valid range or part of a domain or enumerated list?

   + Check for duplicates, for example of a unique key.

   + Check for nulls. Are there mandatory values, or are null / empty values allowed? Are the null types consistent (NaN, infinity, empty strings, etc.)?


- Tips: for duplicates, use function `unique()`. For missing values, use function `is.na()`. To delete all rows with a missing, use function `na.omit()`. Feel free to use other functions to check duplicates and missing values.

```{r}

```

    
# Plot 

- Describe a plot type that you like to create (e.g., barplot, boxplot, scatterplot).


# Post on Discussion Board

- Check your presentation day. 

- Create a post on the discussion board with your presentation title as the post title by 11:59 pm, Feb 15. You'll edit your post on the discussion board to include your presentation files.

- You should upload your presentation files (rmd & html) and dataset you used on the discussion board by the day before your presentation day. For example, if you're a presenter on Feb 21, upload your presentation files by 11:59 pm, Feb 20.  


